---
title: "Get Essential Skills Test Results"
author: "Thomas McManus"
date: "8/13/2019"
output: md_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

`herzog` is an R package designed to automatically scrape Herzog assessment results from the assessment_summary page for your organization. 

## Get results

`get_herzog_results` takes the assessment summary url and returns a data frame where each row is an assessment.

```{r get-results}
devtools::install_github("context-dependent/herzog")

library(tidyverse)
library(herzog)


url <- "https://bpade.essentialskillsgroup.com/custom_reports/assessment_summary.php"

herzog_results <- get_herzog_results(url)

knitr::kable(head(herzog_results))
```


The returned table has 7 meaningful columns: 

- `case_id`: unique identifier for the assessed participant
- `skill`: skill tested. Currently the only skills returned are Document Use and Numeracy, though that will be made flexible in future versions. 
- `test`: whether this is the first (Baseline) or second (Post) test completed by the participant for the skill
- `duration_mins`: how long the test took the participant to complete, rounded to the nearest minute
- `score`: the score achieved on the assessment
- `level`: the category of aptitude associated with the `score`
- `start_date`: the date and time at which the assessment was started


